Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis

### 2015-12-09 paper/EEST/First_Submission/Response/EEST-D-15-00056_response.tex
Final edits to the response to reviewers.

\begin{enumerate}
\item  $Y_{jst} => Y_{ist}$ Change made.

\item  Means now presented instead of total counts.  This was not as simple as divide by the number of traps, since traps were left out for different numbers of days in different months.  Nonetheless, this was a good point.

\item  We doubled checked the calculations and stand by our results.  The correct intervals for November 2011 are (2.7, 7.1) for Diptera and (2.0, 3.9) for Collembola.  The overlap of the intervals is due to large variation in the point estimates, and hence we fail to see the difference between the two point estimates.

\item  ... such long descriptions are not needed.

>>>>

\begin{enumerate}
\item  \textit{$Y_{jst} => Y_{ist}$}
  Change made.

\item  \textit{Fig. 8 shows the total numbers of the preys in the 32 traps. I think the mean (divided by 32) is better because the ratio "c" uses gamma that are close to this mean.}

  Means are now presented instead of total counts.  This was not as simple as divide by the number of traps, since traps were left out for different numbers of days in different months.  Nonetheless, this was a good point.

\item  \textit{In Nov 2011, the MS says there is no significant difference between Collembola and Diptera, but the former looks 1.8-9 (Fig. 10) while the latter looks 3.9-4.0 (Fig. 11). There seems to be a big difference. Isn't it really significant? If not significant, could you explain why?}

  We doubled checked the calculations and stand by our results.  The correct intervals for November 2011 are (2.7, 7.1) for Diptera and (2.0, 3.9) for Collembola.  The overlap of the intervals is due to large variation in the point estimates, and hence we fail to see the difference between the two point estimates.

\item  \textit{... such long descriptions are not needed.}
